The globular cluster system of the Auriga simulations

### 2019-07-10 AurigaGCS.tex
Attempt to motivate each figure, and  explain their take away message for Sec. 4.2

% \citet{2019AJ....157...12B} communicate the latest efforts to aggregate the
% available data, presented in their CatClu catalog. Amongst 10978 star clusters
% and alike objects in the Milky Way, the catalog contains 200 GCs and 94 GC
% candidates. The CatClu catalog contains reference papers, positions, distances,
% and total absolute V magnitude. Therefore we rely on the H96e10 dataset for all
% other quantities, but

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMFeH_withRatios-trim}.png}
    \caption{
        Mass-weighted metallicity distribution of star particles in the Auriga
        simulations. We show the median value of all Auriga haloes for all
        stars (green dotted) and globular cluster candidates (i.e. stars with
        age $>$~10~Gyr; green solid). The latter sub set is further split up
        between stars that formed in-situ (blue solid), and those that were accreted
        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:FeH}
    }
\end{figure}
We now turn to the second goal, which is to see whether sufficient total mass in 
GC candidates produced by the Auriga simulations. To answer this question we plot
a mass-weighted metallicity distribution in Figure~\ref{fig:FeH}. We show the 
median (coloured lines) for all thirty Auriga L4 haloes with the $1\sigma$ 
interval around it (shaded regions, which shows the scatter between runs that 
have different initial conditions, thus, have unique merger histories). We chose 
to aggregate the data to indicate general trends that we find when the GC candidates 
are split up according to birth location, rather than selecting typical examples 
of individual (simulated) galaxies. Once again we notice that the peak metallicity 
shifts down from $0$ to $-0.6$ for old stars (green solid) compared to all stars 
(green dotted), and we learn that the mass at the peak lowers by roughly one dex. 
The mass budget of the old stars is dominated by the old insitu population (blue 
solid) below [Fe/H]~=~$-1$, and by the old accreted stars (red solid) above this 
value. We show the MW (M31) GCS in purple (magenta) and we show the ratio of the 
simulated to the observed profiles in the middle (bottom) panel. This mass excess 
can be thought of the `mass budget' that the Auriga GC candidates can `afford to 
lose' due to a combination of smaller than unity bound cluster formation 
efficiencies combined with a Hubble time of dynamical evolution, while still 
producing a GC system with sufficient mass to be consistent with the MW (M31) GCS. 
The cluster formation efficiency would have to linearly decrease with decreasing 
metallicity for Auriga GC candidates to produce a population of GC candidates 
that is consistent with the MW. For the GC candidates in M31 we find a constant 
mass excess up to $-0.9$, above which the simulations produce a higher mass excess 
with increasing metallicity. If dynamical evolution is not expected to more 
efficiently disrupt GCs of higher metallicity, then we would find that the 
efficiency to form bound star clusters would have to decrease with increasing 
metallicity.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{Rgc_mu_sigma-trim}.png}
    \caption{
        Mean and standard deviation of the radial distribution of star particles
        in each of the thirty Auriga L4 haloes compared to the MW (M31) GCS
        shown in purple (magenta).
        \label{fig:Rgc_mu_sigma}
    }
\end{figure}
Figure~\ref{fig:Rgc_mu_sigma} shows the mean and standard deviation of the
radial distribution of star particles in all Auriga L4 simulations. We notice
that the old insitu populations are much more centrally distributed, whereas
the old accreted component has a larger radial extent. Moreover, the dispersion
increases with increasing mean value of the radial distribution as may be expected
for a non-negative quantity.

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMRgc_withRatios-trim}.png}
    \caption{
        Mass-weighted radial distribution of star particles in the Auriga
        simulations. We show the median value of all Auriga haloes for all
        stars (green dotted) and globular cluster candidates (i.e. stars with
        age $>$~10~Gyr; green solid). The latter sub set is further split up
        between stars that formed in-situ (blue solid), and those that were accreted
        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:Rgc}
    }
\end{figure}
Figure~\ref{fig:Rgc} shows the mass-weighted radial distribution of the
Auriga L4 haloes. We notice a subtle peak around $10$~kpc for all star
particles that is not present for the GC candidates, indicating that the
stellar disc is no longer present when applying the latter selection criterion.
Furthermore, we find that the dominant contribution to the total mass in GC
candidates changes from those formed insitu to the accreted population around
$10$~kpc. Again we show the mass excess of the simulations compared to the Milky
Way and Andromeda GCS. We find a decreasing mass excess with increasing radius
in the range $0.2$ to ${\sim}5$ kpc, followed by an increase attributed
to the accreted subpopulation. We further investigate a breakdown of the total mass
in Auriga GC candidates into bins of both metallicity and radius in the following
section.

>>>>

% \citet{2019AJ....157...12B} communicate the latest efforts to aggregate the
% available data, presented in their CatClu catalog. Amongst 10978 star clusters
% and alike objects in the Milky Way, the catalog contains 200 GCs and 94 GC
% candidates. The CatClu catalog contains reference papers, positions, distances,
% and total absolute V magnitude. Therefore we rely on the H96e10 dataset.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMFeH_withRatios-trim}.png}
    \caption{
        Mass-weighted metallicity distribution of star particles in the Auriga
        simulations. We show the median value of all Auriga haloes for all
        stars (green dotted) and globular cluster candidates (i.e. stars with
        age $>$~10~Gyr; green solid). The latter sub set is further split up
        between stars that formed in-situ (blue solid), and those that were accreted
        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:FeH}
    }
\end{figure}
We now turn to the second goal, which is to see whether sufficient total mass in 
GC candidates produced by the Auriga simulations. To answer this question we plot
a mass-weighted metallicity distribution in Figure~\ref{fig:FeH}. We show the 
median (coloured lines) for all thirty Auriga L4 haloes with the $1\sigma$ 
interval around it (shaded regions, which shows the scatter between runs that 
have different initial conditions, thus, have unique merger histories). We chose 
to aggregate the data to indicate general trends that we find when the GC candidates 
are split up according to birth location, rather than selecting typical examples 
of individual (simulated) galaxies. Once again we notice that the peak metallicity 
shifts down from $0$ to $-0.6$ for old stars (green solid) compared to all stars 
(green dotted), and we learn that the mass at the peak lowers by roughly one dex. 
The mass budget of the old stars is dominated by the old insitu population (blue 
solid) below [Fe/H]~=~$-1$, and by the old accreted stars (red solid) above this 
value. We show the MW (M31) GCS in purple (magenta) and notice that the difference 
between the MW and M31 distributions is substantially larger than the scatter
between different Auriga galaxies, particularly around [Fe/H]~$=-1$. In addition, 
Andromeda does host (a hand full) GCs with [Fe/H]~$< -2.5$ as well as GCs with 
[Fe/H]~$ > 0$ while the Milky Way does not.

We show the ratio of the  simulated to the observed profiles in the middle (bottom) 
panel. This mass excess can be thought of the `mass budget' that the Auriga GC 
candidates can `afford to lose' due to a combination of smaller than unity bound
cluster formation efficiencies combined with a Hubble time of dynamical evolution,
while still producing sufficient mass at the right metallicities. In particular,
the cluster formation efficiency would have to linearly decrease with decreasing 
metallicity for Auriga GC candidates to produce a population of GC candidates 
that is consistent with the MW. For the GC candidates in M31 we find a constant 
mass excess up to $-0.9$, above which the simulations produce a higher mass excess 
with increasing metallicity. If dynamical evolution is not expected to more 
efficiently disrupt GCs of higher metallicity, then we would find that the 
efficiency to form bound star clusters would have to decrease with increasing 
metallicity.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{Rgc_mu_sigma-trim}.png}
    \caption{
        Mean and standard deviation of the radial distribution of star particles
        in each of the thirty Auriga L4 haloes compared to the MW (M31) GCS
        shown in purple (magenta).
        \label{fig:Rgc_mu_sigma}
    }
\end{figure}
We repeat the analysis of the previous subsection for the distribution of
galactocentric radius instead of metallicity. We look for general trends present
in all Auriga L4 galaxies. Figure~\ref{fig:Rgc_mu_sigma} shows the mean and 
standard deviation of the radial distribution of star particles in all Auriga L4 
simulations. We notice that the old insitu populations are more centrally 
distributed, whereas the old accreted subsets have a larger radial extent. This 
is not surprising because the classification of in situ requires star particles 
to have formed within the virial radius, thus they could naturally be expected 
to end up at small galactocentric radii. Accreted star particles, on the other 
hand, have formed in another (sub)halo beyond the virial radius, thus, would 
first have to migrate inwards in order to populate the innermost radii. Moreover, 
we notice that the dispersion increases with increasing mean value of the radial 
distribution as may be expected for a non-negative quantity. The purple (magenta)
cross indicates the values for the MW (M31) GCS, which are to be compared to the
green crosses. The MW GCS lies roughly within the range of values seen for the 
radial distributions produced by the Auriga simulations, whereas the mean of M31
is larger and closer to typical mean values of the accreted GC candidates in
the Auriga simulations. The larger radial extend of the M31 GCS is generally
believed to hint at a more accretion-dominated origin of the GCS, and may reflect
a richer accretion history of the galaxy in comparison to the Milky Way.

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMRgc_withRatios-trim}.png}
    \caption{
        Mass-weighted radial distribution of star particles in the Auriga
        simulations. We show the median value of all Auriga haloes for all
        stars (green dotted) and globular cluster candidates (i.e. stars with
        age $>$~10~Gyr; green solid). The latter sub set is further split up
        between stars that formed in-situ (blue solid), and those that were accreted
        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:Rgc}
    }
\end{figure}
Figure~\ref{fig:Rgc} shows the mass-weighted radial distribution of the
Auriga L4 haloes. We notice a subtle peak around $10$~kpc for all star
particles that is not present for the GC candidates, indicating that the
stellar disc is no longer present when applying the latter selection criterion.
Furthermore, we find that the dominant contribution to the total mass in GC
candidates changes from those formed insitu to the accreted population around
$10$~kpc. Again we show the mass excess of the simulations compared to the Milky
Way and Andromeda GCS. We find a decreasing mass excess with increasing radius
in the range $0.2$ to ${\sim}5$ kpc, followed by an increase attributed
to the accreted subpopulation. For the Milky Way we notice that significantly
fewer GCs are found beyond $40$~kpc than for M31, and that accreted GC candidates
contribute mostly to the Auriga GCS at these radii. We further investigate a 
breakdown of the total mass in Auriga GC candidates into bins of both metallicity 
and radius in the following section.
